Quality assurance of digital twins: An experience report in the automotive industry

### 2023-03-23 manuscripts/paper-1/main.tex
Bug is fixed, pictures are revised, bib is updated

\documentclass{llncs}
\usepackage[colorlinks,allcolors=blue]{hyperref}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{float}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{verbatim}
\usepackage{cite}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{cleveref}
\usepackage{tabularray}
\usepackage{dirtree,array}
\usepackage{subcaption}

@@

    \title{Quality assurance of digital twins -- An experience report in the automotive industry}

@@

    \section{Introduction}\label{section:introduction}

    The notion of the digital twin, which has gained popularity in 
    recent years, is often subject to vague and ambiguous envisions~\cite{Review1}.
    The mispresenting of this notion began with the physical twin of the Apollo 13 spacecraft. 
    The twin of Apollo 13 was merely a tangible replication of the spacecraft that has been utilized in physical simulations. 
    Even though the digital aspect was expected to be present, there wasn't~\cite{GrievesApollo13}.
    Another physical twin is the historic D-day map (also known as the Big Board) in Southwick House England, 
    which was used simultaneously before and during the operation, and can be argued to be similar. 
    The board was a twin of the operation, and it included models of battalions and ships that reflected the actual 
    locations of the corresponding formations. Furthermore, synchronization was 
    implemented to give directives from the real system to control the operation 
    flow and to update the physical twin state~\cite{AMRC}.
    In contrast, a digital twin is a virtual counterpart of a real system, which should 
    be synchronized with a selected frequency and fidelity~\cite{Review1,Review2,digitaltwinconsortium2022}.

    The envision of a digital twin emerged from Grieves'es conceptual model, which was called mirrored spaces model in 2002~\cite{Originsofdigitaltwinconcept},
    and later referenced in a 2005 journal article~\cite{2005JournayArticle}. 
    Furthermore, he introduced the information mirroring model, which was his ideal product lifecycle management tool with only one goal. 
    The goal was to gather enhanced information about the real system to minimize the waste of the system's sources such as energy, 
    time and material. Initially, this model had four main parts. The real system, 
    virtual system, connection between the real and virtual system and virtual simulations~\cite{GrievesPLMBook}. 
    Later, Grieves removed the latter, to simplify the model~\cite{Originsofdigitaltwinconcept}. Lastly, after co-authoring with Vicker in 2010, 
    Grieves decided to use the NASA-invented `Digital Twin' word, instead of the information mirroring model~\cite{Originsofdigitaltwinconcept}.

@@

    The previous studies predominantly focused on the design and implementation of digital twins~\cite{Review1, Review2}. 
    However, a crucial aspect that remains unclear is how to achieve quality in these highly intricate and evolvable systems. 
    Therefore, ascertaining the requisite level of quality of a digital twin is an arduous undertaking that requires further research.

@@

    \section{State of the art on quality}
    The Oxford English Dictionary defines the word `quality' as a noun or an adjective form. The adjective form indicates, 
    a high standard of excellence as in  `quality products`~\cite{OxfordDictionary}. Even though the noun form is defined in multiple ways, the most impactful 
    definition refers to a  standard of an entity that is measured relative to other entities, whether different or similar~\cite{OxfordDictionary}.  
    Additionally, quality is the degree to which a set of inherent properties of an entity fulfills the given requirements~\cite{ISO9000}.
    Both of these definitions clearly show the relative aspect of quality, and the following subcategories are the specialization of these definitions.
    \subsection{Product quality}
    A product is a tangible or intangible system that satisfies the needs or wants of a customer. A product can be a physical system like a car, or an abstract system, like a digital twin. Furthermore, 
    product quality is comprised of two aspects~\cite{GrievesPLMBook}.  
    Firstly, quality is an attribute of a product, which refers to the degree to which a product meets its specifications. These product specifications are mostly defined by the supra-systems' subsystems, such as the stakeholders.
    For this aspect, if the stakeholders' expectations or needs are met,  high quality is considered. The second aspect of product quality is the ability to execute to a specific usage standard.
    Unlike the first aspect, standardization is not controllable. Therefore, the product's quality is determined by how well the implied or obligatory standards are met~\cite{GrievesPLMBook}.

    \subsection{Software quality}
    Software is a combination of programs and data that can be utilized by both virtual and physical systems, 
    such as computer systems\cite{OxfordDictionary}. Its quality is determined by how well it fulfills the requirements that were set. However, 
    those requirements may not always reflect the needs of the stakeholders, hence the quality depends on how accurately these requirements were set~\cite{IEE730-2014}. 
    As an example, ISO/IEC:25010 has standardized eight attributes, 
    including functional suitability, performance efficiency, compatibility, usability, reliability, security, maintainability, and portability, to measure software quality~\cite{ISO/IEC:25010}.

    \subsection{Simulation Quality}
    The human brain simulates real systems abstractly either to predict the future state of the system or to gather information about the past state of the system~\cite{MobusSystemTheory}.
    However, these days, many simulation processes are done by virtual systems. For example, software programs such as ANSYS\cite{Ansys}, ABAQUS\cite{Abaqus}, and AnyLogic\cite{AnyLogic} enable users 
    to build a simulation model to make predictions and get information about the past- as well as the current state of the system.

    Quality characteristics of these simulation models must be evaluated by the validation and verification techniques~\cite{StewartSimulation,VerificationValidationSergent,OsmanBalci}. 
    Validation is the process of evaluating the simulation quality in comparison to the real system from the perspective of its intended applications.
     On the other hand, verification is a procedure to evaluate the implementation of the simulation model and 
    its associated data concerning the conceptual description and specifications of the model developer\cite{StewartSimulation,VerificationValidationSergent}. 
    These techniques are broadly categorized into six areas: informal, static, dynamic, 
    symbolic, constraint, and formal techniques~\cite{balcicategories,balcitechniques}. Formal techniques involve mathematical formality, whereas informal techniques rely on 
    human intervention and reasoning. Although mathematical techniques are more precise, informal techniques are more commonly used~\cite{balcicategories}.

@@

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%METHODS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \section{Method}
    The methodology consists of a set of artifacts, manual artifact reviews, mapping quality attributes to the findings, an evaluation of the artifact quality, and lastly, an evaluation of the digital twin quality.   
    \subsection{Artifacts}\label{section:Artifacts}
    The current stage of review encompasses five key artifacts, including process videos displaying the current assembly procedure without an adaptive workstation and cobot, a scope definition outlining the objects on the shop floor requiring tracking or twinning, a requirements specification summarizing functional and non-functional requirements for the digital twin, a general and an operational conceptual model elucidating the high-level structure of the assembly procedure, 
    and a discrete event simulation module that implements the structures prescribed by the conceptual models.

@@

    \subsection{Manual Artifact Reviews}
    During the initial stages of the project, when the target system was not yet available,
    there was a lack of observable data about system behavior that could be utilized for validation. 
    Instead, informal and potentially incomplete, inconsistent, or incorrect system descriptions had to be relied upon. 
    Therefore, manual reviews were deemed the most suitable tool to account for the characteristics of this situation.
    The manual review included, audits, inspections, reviews, structural analysis and walkthroughs 
    with the project partners which was inspired by Balci's manual review works~\cite{balcitechniques}.

    \subsection{Digital Twin Quality Attributes}\label{section:Digital Twin Quality Attributes}
    To identify the digital twin quality attributes, the following standards, including ISO/IEC:25010, IEE730-2014, ISO9000, and ISO9001, 
    as well as the Oxford dictionary was consulted to 
    synthesize our findings\cite{ISO9000,ISO90012015,ISO/IEC:25010,IEE730-2014, OxfordDictionary}.

@@

    \textbf{Completeness} is a derived word from the word  \textit{complete}, which can be described as an adjective, attribute, or verb\cite{OxfordDictionary}. 
    The adjectival form used in the study denotes \textit{complete} as a state of having all the necessary or appropriate parts according to the real system 
    (Figure~\ref{fig:CorrectnessAndCompleteness}). Additionally, subaspects of completeness, which are \textit{incompleteness} and \textit{overcompleteness} 
    were inspected but identified as a completeness issue.

    \begin{figure}

        \centering
            \includegraphics[width = 1\textwidth]{Correctness and Completeness.png}
            \caption{Incorrect  (a) and incomplete (b) status has been demonstrated with a 
            simplified finite state machine. Incorrectness can be observed in the behavior 
            of the machine after 2 state transitions. Incompleteness, on the other hand, can be observed in 
            the missing state. It should be noted that, even though the second state machine is missing a 
            component, it shows the right behavior, hence it is correct. }\label{fig:CorrectnessAndCompleteness}
    \end{figure}

@@

    \textbf{Efficiency} refers to the quality of being efficient~\cite{OxfordDictionary}. 
    Therefore, \textit{efficiency} is achieving maximum productivity with minimum wasted resources (Figure~\ref{fig:EfficiencyandFidelity}). 
    It is worth mentioning that the concept of \textit{efficiency} is tightly coupled with the notion of productivity, 
    although \textit{efficiency} differs from the latter's definition, which is defined as the capability to produce large amounts of goods~\cite{OxfordDictionary}.  
    For example, time efficiency indicates that,  with less amount of time as an input, more output with the minimum waste during the process is desired (Figure~\ref{fig:EfficiencyandFidelity}).

    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 1\textwidth]{Efficiency and Fidelity.png}
        \caption{Fidelity (a) and efficiency (b) levels have been demonstrated with simplified CAD drawings and 
        finite state machines.}~\label{fig:EfficiencyandFidelity}
    \end{figure}

    \textbf{Evolvability} is a system's capability to enhance its suitability to its environment through alterations to both its internal and functional 
    structure\cite{MobusSystemTheory}. Another term to describe the response to changes in the environment is adaptability.
    However, this concept differs from \textit{evolvability} in that it only affects a system's internal or functional structure temporarily. 
    For instance, a digital twin, which is an evolvable virtual system, can be designed to be more flexible and scalable, 
    allowing for easy updates and the addition of new features\cite{ZHANGUPDATEMETHOD}. 
    Furthermore, the evolvability of the digital twin was assessed based on the quantity of effort, which is a necessary resource to initiate transformation
    within the system (Figure~\ref{fig:Evolvability}).

    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 1\textwidth]{Evolvability.png}
        \caption{Evolvability has been demonstrated with simplified finite state machines. 
        Evolving the machines on the left side, needed effort 
        and the evolved finite state machines on the right side can be observed.}~\label{fig:Evolvability}
    \end{figure}

    \subsection{Mapping Digital Twin Attributes to Manual Review Results}
    To evaluate the quality of the artifact, the issues were mapped to digital twin attributes. 
    To begin this process, the findings were collected from the manual review, followed by an inspection of the findings to determine which digital twin qualities were absent. 
    Finally, the findings were mapped to the relevant missing quality attribute(s) and submitted for artifact quality evaluation (Figure~\ref{fig:Method}).

    \subsection{Artifact Quality Evaluation}
    To evaluate the quality of the digital twin artifacts, the mapped findings were scrutinized and evaluated. 
    The process started by identifying which quality attribute(s) were mapped. 
    Once identified, the missing attribute(s) was incremented by 1 to determine the total quality of missing attributes of the artifact(Figure~\ref{fig:Method}).

    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 0.8\textwidth]{RequirementSpecifications.png}
        \caption{Method for the evaluation of the digital twin artifact quality: Artifact. finding indicates that the finding belongs to the artifact, while -> indicates mapping}\label{fig:Method}
    \end{figure}

    \subsection{Digital Twin Quality Evaluation}
    To determine the quality of the digital twin, 
    the values obtained from evaluating each artifact's quality were collected and summed. 
    Furthermore, the value of the sum was assigned to the related digital twin quality attribute. 
    As a result, the digital twin quality was demonstrated with quality attribute values (Figure~\ref{fig:MethodforDigitalTwinQuality}).

    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 0.8\textwidth]{DigitalTwinQuality.png}
            \caption{Method for the evaluation of the digital twin quality}\label{fig:MethodforDigitalTwinQuality}
    \end{figure}

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%RESULTS%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \section{Results}

    First, to assess digital twin quality,
    manual reviews for each artifact were conducted (Figure~\ref{fig:QualityInspectonResultsWithArtifacts} ). 
    As a result, a total of twenty-one quality issues were identified,
    listed, and finally mapped to the digital twin quality attributes(Table~\ref{tab:Table1})(Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).
    The mapping process 
    revealed that a total of thirty-eight digital twin quality attributes were 
    lacking in the artifacts(Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).  
    Specifically, 23\% of the quality issues of the digital twin were related to correctness, 
    which indicates an error between the real- and digital twin system. Furthermore, 36\%  were related 
    to completeness, proving that some necessary or appropriate parts were missing.
    Moreover, 8\%  were related to fidelity, indicating a lack of detail. 
    In addition, 5\%  were related to efficiency, indicating poor performance or excessive resource usage.
    And finally, 28\% were related to evolvability, indicating that the system was unresponsive 
    to the environment and was not flexible or scalable.

    \subsection{Example Findings}  
    Two examples(Finding 12, Finding 18) are given to the reader to illustrate 
    the results of the manual review as well as the mapping to the digital twin quality attributes.

@@

    The duration of the micro-operations in the conceptual model was calculated using a simple calculation 
    scheme based on the duration of the corresponding macro-operations,
     which were well-known from a prior well-conducted study. 
    However, relying on estimated, 
    simplified calculations for the micro-operation durations,
    suggests that the digital twin conceptual model suffers from issues of correctness and completeness(Table~\ref{tab:Table1}) .

    \subsubsection{Simulation Model-Finding 18:}
        The discrete event simulation model enforced a strictly sequential execution of micro-operations,
        which precludes the support of parallel execution. 
        However, machine-human collaboration on a task, needs a parallel execution, especially when the cobot overtakes certain micro-operations. 
        Thus, the exclusion of parallel executions indicates that the simulation model was incomplete,
        at the same time, using the wrong type of execution highlights its inaccuracies(Table~\ref{tab:Table1}) .

    \begin{figure}[htbp]
            \centering
            \includegraphics[scale = 0.35]{quality_inspection_results_with_artifacts.png}
            \caption{Quality Inspection Results Categorized with Artifacts: X-Axis represents artifacts in section~\ref{section:Artifacts}, 
            Y-Axis represents the number of missing quality attributes found for each artifact, 
            and lastly, each digital twin quality attribute is shown by the colors.}\label{fig:QualityInspectonResultsWithArtifacts}
    \end{figure}

@@

    \scalebox{0.80}{

@@

    This paper aimed to evaluate the quality issues with the given digital twin system in the FELICE project while enhancing the 
    scientific understanding of the quality of digital twins. As a result, this study demonstrates the idea of doing a manual review and mapping 
    quality attributes to issues as a suitable approach for evaluating the quality of digital twins in the design phase. Furthermore, 
    the study suggests that this evaluation is an effective way to collect information about the strengths and weaknesses of the digital twin system.
    Although the findings should be interpreted with caution, collected information can be used to improve the upcoming design decisions, consequently to higher-quality digital twin systems.

@@

    It would be interesting to map the risks of the issues instead of the issues to the quality attributes. 
    The risk mapping approach includes severity and priority variables, which would include the perspective of the stakeholders~\cite{CemKanerSoftwareTesting, ISO/IEC/IEEE29119}.
    As a result, quality attributes can be weighted regarding the stakeholder needs.  This aspect might be important because of relativity, 
    more specifically the political and economical nature of the quality~\cite{SystemQuality}.

    \section*{Acknowledgements}
    %TODO

>>>>

\documentclass{llncs}
\usepackage[colorlinks,allcolors=blue]{hyperref}
\usepackage[T1]{fontenc}
\usepackage{bookmark}
\usepackage{graphicx}
\usepackage{dirtree,array}
\usepackage{tabularray}

@@

    \title{Quality assurance of digital twins: An experience report in the automotive industry}

@@

    \section{Introduction}\label{section:introduction}
    The notion of the digital twin, which has gained popularity in recent years, is often subject to vague and ambiguous envisions~\cite{Review1}.
    The mispresenting of this notion began with the physical twin of the Apollo 13 spacecraft. 
    The twin of Apollo 13 was merely a tangible replication of the spacecraft that has been utilized in physical simulations. 
    Even though the digital aspect was expected to be present, there wasn't~\cite{GrievesMichaelApolloMyth}.
    Another physical twin is the historic D-day map (also known as the Big Board) in Southwick House England, 
    which was used simultaneously before and during the operation, and can be argued to be similar. 
    The board was a twin of the operation, and it included models of battalions and ships that reflected the actual 
    locations of the corresponding formations. Furthermore, synchronization was 
    implemented to give directives from the real system to control the operation 
    flow and to update the physical twin state~\cite{AMRC}.
    In contrast, a digital twin is a virtual counterpart of a real system, which should 
    be synchronized with a selected frequency and fidelity~\cite{Review1,Review2,digitaltwinconsortium2022}.

    The envision of a digital twin emerged from Grieves'es conceptual model, which was called mirrored spaces model in 2002~\cite{Originsofdigitaltwinconcept},
    and later referenced in a 2005 journal article~\cite{2005ArticleGrievesMichael}. 
    Furthermore, he introduced the information mirroring model, which was his ideal product lifecycle management tool with only one goal. 
    The goal was to gather enhanced information about the real system to minimize the waste of the system's sources such as energy, 
    time and material. Initially, this model had four main parts. The real system, 
    virtual system, connection between the real and virtual system and virtual simulations~\cite{GrievesPLMBook}. 
    Later, Grieves removed the latter, to simplify the model~\cite{Originsofdigitaltwinconcept}. Lastly, after co-authoring with Vicker in 2010, 
    Grieves decided to use the NASA-invented `Digital Twin' word, instead of the information mirroring model~\cite{Originsofdigitaltwinconcept}.

@@

    The previous studies predominantly focused on the design and implementation of digital twins~\cite{Review1,Review2}. 
    However, a crucial aspect that remains unclear is how to achieve quality in these highly intricate and evolvable systems. 
    Therefore, ascertaining the requisite level of quality of a digital twin is an arduous undertaking that requires further research.

@@

    \section{Related Work on Quality}
    The notion of quality is defined in many forms in the literature. Some scholars defined quality as conformance to specifications and
    requirements~\cite{ProductConformanceCostGilmore,LevittTheodoreProduction-LineApproach,QualityisFree}, while others saw it as a value~\cite{QualityandCompetitionanEssayinEconomicTheory} or the 
    fitness for use~\cite{Juran1974}which evolved to fitness for purpose later~\cite{Juran2010},  
    or an abstain of loss~\cite{GenichiTaguchi}, and meeting or exceeding customer expectations~\cite{Groenrossstrategicmanagementandmarketing}. 
    Even the ISO9000 standard defines the quality differently, which is an inherent characteristic of the entity~\cite{ISO9000}. 
    These definitions endeavors to provide an universal understanding of quality and assess it subsequently. However, 
    they come with some strengths and weaknesses. For example, conforming to the requirements and specifications can be useful for assessing the quality of the system but may not always reflect the needs of the stakeholders,
    hence the quality of the system depends on how accurately these requirements were set~\cite{IEE7302014}.

    The first serious discussions of subcategorization of quality trace back to the beginning of the 20th century with the emergence of product-focused quality management practices in manufacturing~\cite{HistoryofControlEngineering}.
    Later on, with the development of new technologies, subcategorization of quality was evolved and extended to other areas, such as software, which appeared in the 1970s~\cite{ThePsychologyofComputerProgramming}.
    With this emergence, assessing the software quality became inevitable and as a result, a considerable amount of software quality models and characteristics have been established~\cite{SoftwareQualityModels,Charecteristicsofsoftwarequality,AnActivityBasedQualityModelforMaintainability}.
    As an example, ISO/IEC:25010 has standardized eight software quality characteristics, including functional suitability, performance efficiency, compatibility, usability, reliability, security, maintainability, 
    and portability, to determine software quality~\cite{ISO/IEC:25010}.

    It was not until the late 1950s that another important subcategory for the context of this paper `computer simulation quality' 
    was considered~\cite{SomeProblemsofDigitalSystemsSimulation}. Surprisingly, R. W. Conway et al.identified several potential problems with computer simulation systems in this era, which are still relevant today.  
    To find and evaluate these problems, validation and verification techniques have emerged~\cite{StewartSimulation,VerificationValidationSergent,OsmanBalci}. 
    Validation is the process of evaluating the simulation quality in comparison to the real system from the perspective of its intended applications. 
    On the other hand, verification is a procedure to evaluate the implementation of the simulation model and its associated data concerning the conceptual description and specifications of 
    the model developer~\cite{StewartSimulation,VerificationValidationSergent}. These techniques are broadly categorized into six areas: informal, static, dynamic, symbolic, constraint, 
    and formal techniques~\cite{balcicategories,balcitechniques}. Formal techniques involve mathematical formality, 
    whereas informal techniques rely on human intervention and reasoning. Although mathematical techniques are more precise, informal techniques are more commonly used~\cite{balcicategories}.

@@

    \section{Method}
    The methodology consists of a set of artifacts, manual artifact reviews, mapping quality attributes to the findings, an evaluation of the artifact quality, and lastly, an evaluation of the digital twin quality.   
    \subsection{Artifacts}\label{section:Artifacts}
    The current stage of review encompasses five key artifacts, including process videos displaying the current assembly procedure without an adaptive workstation and cobot, a scope definition outlining the objects on the shop floor requiring tracking or twinning, a requirements specification summarizing functional and non-functional requirements for the digital twin, a general and an operational conceptual model elucidating the high-level structure of the assembly procedure, 
    and a discrete event simulation module that implements the structures prescribed by the conceptual models.

@@

    \subsection{Manual Artifact Reviews}
    During the initial stages of the project, when the target system was not yet available,
    there was a lack of observable data about system behavior that could be utilized for validation. 
    Instead, informal and potentially incomplete, inconsistent, or incorrect system descriptions had to be relied upon. 
    Therefore, manual reviews were deemed the most suitable tool to account for the characteristics of this situation.
    The manual review included audits, inspections, reviews, structural analysis and walkthroughs 
    with the project partners which was inspired by Balci's manual review works~\cite{balcitechniques}.

    \subsection{Digital Twin Quality Attributes}\label{section:Digital Twin Quality Attributes}
    To identify the digital twin quality attributes, the following standards, including ISO/IEC:25010, IEE730-2014, ISO9000, and ISO9001, 
    as well as the Oxford dictionary was consulted to 
    synthesize our findings\cite{ISO9000,ISO90012015,ISO/IEC:25010,IEE7302014,OxfordDictionary}.

@@

    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 1\textwidth]{CorrectnessandCompleteness.png}
        \caption{Incorrect (a) and incomplete (b) status has been demonstrated with a simplified finite state machine. Incorrectness can be observed in the behavior 
        of the machine after 2 state transitions. Incompleteness, on the other hand, can be observed in the missing state. It should be noted that, even though the second state machine is missing a 
        component, it shows the right behavior, hence it is correct.}\label{fig:CorrectnessAndCompleteness}
    \end{figure}

    \textbf{Completeness} is a derived word from the word  \textit{complete}, which can be described as an adjective, attribute, or verb~\cite{OxfordDictionary}. 
    The adjectival form used in the study denotes \textit{complete} as a state of having all the necessary or appropriate parts according to the real system 
    (Figure~\ref{fig:CorrectnessAndCompleteness}). Additionally, subaspects of completeness, which are \textit{incompleteness} and \textit{overcompleteness} 
    were inspected but identified as a completeness issue.

@@

    \textbf{Efficiency} refers to the quality of being efficient~\cite{OxfordDictionary}. 
    Therefore, \textit{efficiency} is achieving maximum productivity with minimum wasted resources (Figure~\ref{fig:EfficiencyandFidelity}). 
    It is worth mentioning that the concept of \textit{efficiency} is tightly coupled with the notion of productivity, 
    although \textit{efficiency} differs from the latter's definition, which is defined as the capability to produce large amounts of goods~\cite{OxfordDictionary}.  
    For example, time efficiency indicates that,  with less amount of time as an input, more output with the minimum waste during the process is desired (Figure~\ref{fig:EfficiencyandFidelity}).
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 1\textwidth]{Efficiency and Fidelity.png}
        \caption{Fidelity (a) and efficiency (b) levels have been demonstrated with simplified CAD drawings and 
        finite state machines.}~\label{fig:EfficiencyandFidelity}
    \end{figure}
    \textbf{Evolvability} is a system's capability to enhance its suitability to its environment through alterations to both its internal and functional 
    structure\cite{MobusSystemTheory}. Another term to describe the response to changes in the environment is adaptability.
    However, this concept differs from \textit{evolvability} in that it only affects a system's internal or functional structure temporarily. 
    For instance, a digital twin, which is an evolvable virtual system, can be designed to be more flexible and scalable, 
    allowing for easy updates and the addition of new features\cite{ZHANGUPDATEMETHOD}. 
    Furthermore, the evolvability of the digital twin was assessed based on the quantity of effort, which is a necessary resource to initiate transformation
    within the system (Figure~\ref{fig:Evolvability}). 
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 1\textwidth]{Evolvability.png}
        \caption{Evolvability has been demonstrated with simplified finite state machines. 
        Evolving the machines on the left side, needed effort 
        and the evolved finite state machines on the right side can be observed.}~\label{fig:Evolvability}
    \end{figure}
    \subsection{Mapping Digital Twin Attributes to Manual Review Results}
    To evaluate the quality of the artifact, the issues were mapped to digital twin attributes. 
    To begin this process, the findings were collected from the manual review, followed by an inspection of the findings to determine which digital twin qualities were absent. 
    Finally, the findings were mapped to the relevant missing quality attribute(s) and submitted for artifact quality evaluation (Figure~\ref{fig:Method}).
    \subsection{Artifact Quality Evaluation}
    To evaluate the quality of the digital twin artifacts, the mapped findings were scrutinized and evaluated. 
    The process started by identifying which quality attribute(s) were mapped. 
    Once identified, the missing attribute(s) was incremented by 1 to determine the total quality of missing attributes of the artifact(Figure~\ref{fig:Method}).
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 0.8\textwidth]{RequirementSpecifications.png}
        \caption{Method for the evaluation of the digital twin artifact quality: `Artifact.finding' indicates that the finding belongs to the artifact, while `->' indicates mapping}\label{fig:Method}
    \end{figure}
    \subsection{Digital Twin Quality Evaluation}
    To determine the quality of the digital twin, 
    the values obtained from evaluating each artifact's quality were collected and summed. 
    Furthermore, the value of the sum was assigned to the related digital twin quality attribute. 
    As a result, the digital twin quality was demonstrated with quality attribute values (Figure~\ref{fig:MethodforDigitalTwinQuality}).
    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 0.8\textwidth]{DigitalTwinQuality.png}
            \caption{Method for the evaluation of the digital twin quality}\label{fig:MethodforDigitalTwinQuality}
    \end{figure}
    \section{Results}
    First, to assess digital twin quality, manual reviews for each artifact were conducted (Figure~\ref{fig:QualityInspectonResultsWithArtifacts}). 
    As a result, a total of twenty-one quality issues were identified, listed, and finally mapped to the digital twin quality attributes (Table~\ref{tab:Table1}) (Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).
    The mapping process revealed that a total of thirty-eight digital twin quality attributes were lacking in the artifacts (Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).  
    Specifically, 23\% of the quality issues of the digital twin were related to correctness, which indicates an error between the real- and digital twin system. Furthermore, 36\%  were related 
    to completeness, proving that some necessary or appropriate parts were missing.
    Moreover, 8\%  were related to fidelity, indicating a lack of detail. 
    In addition, 5\%  were related to efficiency, indicating poor performance or excessive resource usage.
    And finally, 28\% were related to evolvability, indicating that the system was unresponsive 
    to the environment and was not flexible or scalable.
    \subsection{Example Findings}  
    Two examples(Finding 12, Finding 18) are given to the reader to illustrate 
    the results of the manual review as well as the mapping to the digital twin quality attributes. 

@@

    The duration of the micro-operations in the conceptual model was calculated using a simple calculation 
    scheme based on the duration of the corresponding macro-operations,
     which were well-known from a prior well-conducted study. 
    However, relying on estimated, 
    simplified calculations for the micro-operation durations,
    suggests that the digital twin conceptual model suffers from issues of correctness and completeness (Table~\ref{tab:Table1}). 
    \subsubsection{Simulation Model-Finding 18:}
        The discrete event simulation model enforced a strictly sequential execution of micro-operations,
        which precludes the support of parallel execution. 
        However, machine-human collaboration on a task, needs a parallel execution, especially when the cobot overtakes certain micro-operations. 
        Thus, the exclusion of parallel executions indicates that the simulation model was incomplete,
        at the same time, using the wrong type of execution highlights its inaccuracies (Table~\ref{tab:Table1}).
    \begin{figure}[htbp]
            \centering
            \includegraphics[scale = 0.35]{quality_inspection_results_with_artifacts.png}
            \caption{Quality Inspection Results Categorized with Artifacts: X-Axis represents artifacts in section \ref{section:Artifacts}, 
            Y-Axis represents the number of missing quality attributes found for each artifact, 
            and lastly, each digital twin quality attribute is shown by the colors.}\label{fig:QualityInspectonResultsWithArtifacts}
    \end{figure}

@@

        \scalebox{0.75}{

@@

    This paper aimed to evaluate the quality issues with the given digital twin system in the FELICE project while enhancing the 
    scientific understanding of the quality of digital twins. As a result, this study demonstrates the idea of doing a manual review and mapping 
    quality attributes to issues as a suitable approach for evaluating the quality of digital twins in the design phase. Furthermore, 
    the study suggests that this evaluation is an effective way to collect information about the strengths and weaknesses of the digital twin system.
    Although the findings should be interpreted with caution, collected information can be used to improve the upcoming design decisions, consequently to higher-quality digital twin systems.

@@

    It would be interesting to map the risks of the issues instead of the issues to the quality attributes. 
    The risk mapping approach includes severity and priority variables, which would include the perspective of the stakeholders~\cite{CemKanerSoftwareTesting,ISO/IEC/IEEE29119}.
    As a result, quality attributes can be weighted regarding the stakeholder needs. This aspect might be important, because of relativity, 
    more specifically due to the political and economical nature of the quality~\cite{SystemQuality}. 
    \section*{Acknowledgements}
